\chapter*{Tài liệu tham khảo}
\addcontentsline{toc}{chapter}{Tài liệu tham khảo}

\begin{thebibliography}{99}

\bibitem{openmp_spec}
OpenMP Architecture Review Board.
\textit{OpenMP Application Programming Interface Specification, Version 5.2}.
OpenMP ARB, 2021.
\texttt{https://www.openmp.org/specifications/}

\bibitem{parallel_programming_openmp}
Chapman, B., Jost, G., \& van der Pas, R.
\textit{Using OpenMP: Portable Shared Memory Parallel Programming}.
The MIT Press, 2008. ISBN: 978-0-262-53302-7.

\bibitem{introduction_parallel_computing}
Grama, A., Kumar, V., Gupta, A., \& Karypis, G.
\textit{Introduction to Parallel Computing} (2nd ed.).
Addison-Wesley, 2003. ISBN: 978-0-201-64865-2.

\bibitem{parallel_programming_in_science}
Hager, G., \& Wellein, G.
\textit{Introduction to High Performance Computing for Scientists and Engineers}.
CRC Press, 2010. ISBN: 978-1-4398-1192-4.

\bibitem{numerical_linear_algebra}
Trefethen, L. N., \& Bau, D.
\textit{Numerical Linear Algebra}.
SIAM, 1997. ISBN: 978-0-898-71361-9.

\bibitem{amdahl_law}
Amdahl, G. M.
\textit{Validity of the single processor approach to achieving large scale computing capabilities}.
In \textit{Proceedings of the AFIPS Spring Joint Computer Conference}, pp.~483--485, 1967.
\texttt{https://doi.org/10.1145/1465482.1465560}

\bibitem{matrix_algorithms}
Golub, G. H., \& Van Loan, C. F.
\textit{Matrix Computations} (4th ed.).
Johns Hopkins University Press, 2013. ISBN: 978-1-421-40859-0.

\bibitem{cache_aware_algorithms}
Frigo, M., Leiserson, C. E., Prokop, H., \& Ramachandran, S.
\textit{Cache-oblivious algorithms}.
In \textit{Proceedings of the 40th Annual Symposium on Foundations of Computer Science (FOCS)}, pp.~285--297, 1999.

\bibitem{superscalar_cache}
Drepper, U.
\textit{What Every Programmer Should Know About Memory}.
Red Hat Inc., 2007.
\texttt{https://www.akkadia.org/drepper/cpumemory.pdf}

\end{thebibliography}

